\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-09-24 papers/methods/paper.tex
More feedback

These results show that both BBC and BHM are sensitive to the intrinsic scatter model, finding differences of $\sim0.06$ in $w$ when varying the scatter model. The BBC method finds $w$ biased low for G10 and $w$ biased high for C11 (by about $\pm0.03$), so taking the average result only results in a small bias of $-0.01$ in $w$. Our method shows a small (but not statistically significant) improvement in the insensitivity to the intrinsic scatter model, finding no bias for {\gten} but a $w$ biased high for {\celeven}. The average bias over the two scatter models is $+0.028$, representing a larger bias than the BBC method.

>>>>

{\green As shown in GET-BROUT-CITATION, BBC recovers cosmological parameters without bias so long as the intrinsic scatter model is known. As we do not know the correct intrinsic scatter model, the BBC method averages the results when using bias corrections from {\gten} and from {\celeven}. As such, we expect the BBC method to be biased in one direction for {\gten} simulations and the other direction for {\celeven} simulations. These results are consistent with those displayed in Table \ref{tab:bulk_summary_bbc}, as both} BBC and BHM are sensitive to the intrinsic scatter model, finding differences of $\sim0.06$ in $w$ when varying the scatter model. The BBC method finds $w$ biased low for G10 and $w$ biased high for C11 (by about $\pm0.03$), so taking the average result only results in a small bias of $-0.01$ in $w$. Our method shows a small improvement in the insensitivity to the intrinsic scatter model, finding no bias for {\gten} but a $w$ biased high for {\celeven}. This decrease in error is not statistically significant as we have statistical uncertainty of $\sim0.01$ for $100$ simulation realisations. The average bias over the two scatter models is $+0.028$, representing a larger bias than the BBC method.
